%-------------------------
% Resume in Latex
% Author : Giridhar Kumar
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.6in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}
{\vspace{-3pt}\scshape\raggedright\normalsize\bfseries}
{}{0em}{}[\titlerule \vspace{-4pt}]

\pdfgentounicode=1

% Commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.12in,label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\newcommand{\resumeItem}[1]{\item \small{#1}}

\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textbf{\small #2} \\
\textit{#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\small #1} & \textit{\small #2} \\
\end{tabular*}
}

\begin{document}

\begin{center}
{\LARGE \scshape Giridhar Kumar} \\

Bangalore, India \\

\small
\href{tel:8969485658}{\faPhone\ 8969485658} \quad
\href{mailto:giridhar.sharma.web@gmail.com}{\faEnvelope\ giridhar.sharma.web@gmail.com
} \quad
\href{https://linkedin.com/in/kumar-giridhar}{\faLinkedin\ linkedin.com/in/kumar-giridhar} \quad
\href{https://github.com/giridhar-bot}{\faGithub\ github.com/giridhar-bot}
\end{center}




% SUMMARY
\section{Summary}
Full Stack Engineer with 4.6+ years of experience building scalable microservices-based enterprise applications using Java, Spring Boot, and React.js. Strong in API design, performance optimization, caching strategies, and distributed workflow automation.

% SKILLS
\section{Technical Skills}
\resumeItemListStart
\resumeItem{\textbf{Frontend:} React.js, Redux, Context API, Material UI, JavaScript, TypeScript, Responsive UI Design}
\resumeItem{\textbf{Backend:} Java, Spring Boot, Microservices , REST APIs, Redis, SQL, Multithreading, Async Processing, JWT/Spring Security}
\resumeItem{\textbf{Tools \& Core:} Docker, Git, GitHub Copilot, CI/CD, Postman, Data Structures \& Algorithms, OOP, System Design, DB Indexing,}
\resumeItemListEnd

% EXPERIENCE
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Capgemini}{Dec 2025 -- Present}
{Consultant – Full Stack Engineer (Java + React)}{Bangalore, India}

\resumeItemListStart
\resumeItem{Client: \textbf{Mercedes-Benz Research \& Development India (MBRDI)}}
\resumeItem{Developing microservices-based IT Controlling platform for financial planning, cost allocation, and IT service billing automation.}
\resumeItem{Designed REST APIs integrating enterprise workflow (C-FMP → ServCat → Billing4IT) ensuring seamless cross-system data flow.}
\resumeItem{Reduced manual financial processing efforts by automating approval and billing workflows across multiple internal platforms.}
\resumeItem{Improved API performance and reliability using async processing and optimized SQL queries.}
\resumeItem{Built a dynamic Hierarchy Management module with Spring Boot backend and React-based UI for multi-level structures, target mapping, and secure CRUD/batch operations.}
\resumeItemListEnd

\resumeSubheading
{Infinite Computer Solutions}{Jul 2021 -- Sept 2025}
{Software Engineer – Java Full Stack (Java + React  )}{Bangalore, India}

\resumeItemListStart
\resumeItem{Led end-to-end development of scalable enterprise applications using Java, Spring Boot, and React.js.}
\resumeItem{Designed and developed RESTful microservices handling billing, order tracking, and reporting workflows serving 15K+ monthly transactions.}
\resumeItem{Improved backend response time by 40\% using Redis caching, async processing (CompletableFuture), and optimized DB indexing.}
\resumeItem{Built reusable React component libraries (forms, dashboards, tables) improving UI development speed by 30\%.}
\resumeItem{Enhanced front-end performance using code splitting, lazy loading, and memoization reducing load time by 40\%.}
\resumeItemListEnd

\resumeSubHeadingListEnd


% PROJECTS
\section{Projects}
\resumeSubHeadingListStart

\resumeSubSubheading
{IT Controlling (ITC) Platform | Mercedes-Benz Research \& Development India}{Dec 2025 -- Present}
\resumeItemListStart
\resumeItem{Enterprise financial management platform enabling IT service planning, cost allocation, and billing automation.}
\resumeItem{Improved financial process automation and reduced manual intervention through system integration.}
\resumeItemListEnd
\resumeSubSubheading
{Enterprise Customer Portal | Brightspeed}{Mar 2024 -- Sept 2025}
\resumeItemListStart
\resumeItem{Built scalable portal handling 15K+ monthly transactions (billing, orders, ticketing) using Spring Boot microservices and React.}
\resumeItem{Optimized APIs and DB queries improving performance and ensuring secure role-based access control.}
\resumeItemListEnd


\resumeSubSubheading
{Smart Analytics System | Verizon}{Jul 2022 -- Feb 2024}
\resumeItemListStart
\resumeItem{Developed real-time 4G/5G network analytics dashboards with optimized backend APIs and interactive visualization.}
\resumeItem{Improved large dataset rendering performance through efficient data-fetching and query tuning.}
\resumeItemListEnd


\resumeSubSubheading
{Drone Monitoring Platform | Qualcomm}{Aug 2021 -- Jun 2022}
\resumeItemListStart
\resumeItem{Engineered real-time telemetry processing system with map-based live tracking and backend data services.}
\resumeItem{Designed scalable REST APIs supporting concurrent data ingestion and monitoring workflows.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% CERTIFICATIONS
\section{Certifications}
\resumeItemListStart
\resumeItem{\href{https://www.hackerrank.com/certificates/iframe/24f069b86e78}{Front-end Developer (React) – HackerRank (Jun 2024)}}
\resumeItem{\href{https://www.hackerrank.com/certificates/iframe/797ced8fb9ab}{Java (Basic) Certificate – HackerRank (Oct 2024)}}
\resumeItemListEnd

% ACHIEVEMENTS
\section{Achievements}
\resumeItemListStart
\resumeItem{Performer of the Month (Jul 2023): Recognized for redesigning legacy UI layouts achieving 100\% responsiveness.}
\resumeItemListEnd

\end{document}
